% Copyright 2011-2012, Giampiero Salvi <giampi@kth.se>
\usepackage[utf8]{inputenc}
\usepackage{multicol}

\title{Audio-Visual Speech Processing 2011}
\date{Aug 31 -- Sep 3, 2011}
\address{Volterra, Italy}

\editor{Giampiero Salvi, Jonas Beskow, Olov Engwall, Samer Al Moubayed}
\school{KTH, Computer Science and Communication\\ Department of Speech, Music and Hearing\\SE-100 44 Stockholm, Sweden}
\issn{1680-8908}

\makeindex

\begin{document}
\pagenumbering{roman}
\maketitle
%\cleardoublepage
\newpage
\section*{Foreword}\addcontentsline{toc}{section}{Foreword}
Welcome to the International Conference on Auditory-Visual Speech Processing (AVSP) 2011. Sixteen years ago in Bonas, France, the workshop on \emph{Speech reading my man and machine} gathered an interdisciplinary group of researchers involved in various aspects of auditory-visual speech processing. The Bonas workshop may be seen as the start of a long series of meetings in this relatively new research field, since 1997 under the flag of \emph{AVSP}. These meetings have held on to the interdisciplinary spirit of the Bonas workshop, and just as Bonas they have often taken place in more or less isolated countryside locations somewhat tricky to get to (and away from). We believe this is an important factor leading to the creative and familiar atmosphere that has been a trademark of the AVSP conferences.

We hope that this years AVSP, which is the 11\textsuperscript{th} in the series, will be no exception in this respect.  The SIAF (International Executive Campus) Learning Village in Volterra, Tuscany, is idyllically situated in the Tuscan countryside, offering a panoramic view of the sea, and just a short distance from the historical hilltop town of Volterra. The conference is organised by the Department of Speech, Music and Hearing, KTH, Stockholm, Sweden.

These proceedings contain the 28 papers accepted for presentation at AVSP 2011, of which 3 are demo papers. The total number of submissions was 33. The reviewing process required that each paper receive at least two reviews (mostly three reviewers have judged each papers). We are grateful to all of the reviewers listed overleaf for providing their valuable time. 

Additionally, in our programme we have two exceptional invited speakers: Sverre Sjölander --- Professor Emeritus in Zoology, Linköping University, Sweden and Colm Massey --- Head of research and development at AudioMotion, Oxford, UK. In recent years, AVSP keynote speakers have given a good overview about human audiovisual speech processing. In our opinion, Sverre Sjölander's talk can put this subject into a broader perspective, and provide the background for discussions on what is specific for human audiovisual speech processing and what is more general perception. On the other hand, Colm Massey's talk will address the ever growing field of truthful animation of human motion for computer gaming and entertainment. Because this has become a truly important part of society, we believe the AVSP participant will find it interesting to explore how realistic visual speech for computer games is to date, where the bottlenecks are, and what lies ahead in research and development. We believe the keynote speaker's contributions will fit the theme of the conference, where fundamental research in human behaviour and perception meets the more applied research and development in the entertainment industry. 

We are also pleased that AVSP 2011, as with previous years, has attracted a truly interdisciplinary group of delegates. We have papers relating to speech and gesture, speech perception, audiovisual speech synthesis, audiovisual speech recognition and robotics. We encourage participants to take advantage of this heterogeneous group of delegates together with the unique setting of AVSP conferences, where the common meals and the small size of the conference make many fruitful discussions possible. We hope that you have an enjoyable conference and find the time to visit some of the wonderful sites in and around Volterra.

\vspace{1cm}
\noindent The AVSP 2011 organising committee

\noindent Stockholm, August 2011.

\newpage
\section*{Referees}\addcontentsline{toc}{section}{Referees}
\begin{itemize}
\item Gerard Bailly (GIPSA)
\item Denis Burnham (MARCS)
\item Piero Cosi (ISTC CNR - UOS PADOVA)
\item Darren Cosker (U. BATH)
\item Sacha Fagel (ZOOBE)
\item Gabriele Fanelli (ETZH)
\item Björn Granström (KTH)
\item Valerie Hazan (UCL)
\item David House (KTH)
\item Carlos Ishi (ATR)
\item Alexandra Jesse (UMASS AMHERST)
\item Christian Kroos (MARCS)
\item Francisco Lacerda (STOCKHOLM U.)
\item Dominic W. Massaro (UCSC)
\item Slim Ouni (LORIA)
\item Catherine Pelachaud (PARIS TECH)
\item Gerasimos Potamianos (NCSR ``Demokritos'')
\item Laurel Riek (CAMBRIDGE)
\item Kaoru Sekiyama (U. KUMAMOTO)
\item Marc Swerts (Tilburg U.)
\item Barry-John Theobald (UEA)
\end{itemize}
%\cleardoublepage
\newpage
\tableofcontents

\cleardoublepage
% Keynote speakers
\pagenumbering{arabic}
\refstepcounter{section}\addcontentsline{toc}{section}{Invited papers}
\includepaper{Acoustical and visual processing in the animal kingdom}{Sverre Sj{\"o}lander}{keynote_sverre/keynote_sverre}
\includepaper{From Actor To Avatar: Real world challenges in capturing the human face}{Colm Massey}{keynote_colm/keynote_colm}

\cleardoublepage
% rest of papers
\refstepcounter{section}\addcontentsline{toc}{section}{Reviewed papers}
\input{papers}

\section*{Author Index}\addcontentsline{toc}{section}{Author Index}
\begin{multicols}{2}
\printauthorindex
\end{multicols}
\end{document}


% do not remove (emacs configuration)
% Local variables:
% enable-local-variables: t
% ispell-local-dictionary: "en_GB"
% mode: flyspell
% eval: (flyspell-buffer)
% End:
